Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-07 Ben_Manuscripts/Paper1/Outline.tex
Adding questions

  We do not know the number of monomers that constitute the layers which stack
  on top of each other to create pores.
  \begin{itemize}
%     \item The Col\textsubscript{h} phase is described as having pores made of
%     disks or layers stacked on top of one another, each containing a set 
%     number of monomers. 
    \item A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model has the best chance of directly answering this question.
  \end{itemize}
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how

    Even if we knew the number of monomers in each layer, we still would not know how 
    monomers in each layer are positioned with respect to other layers. 
    \begin{itemize}
      \item A driving force of self assembly in this system is thought to be pi-pi
      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
    \end{itemize}

@@

  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally
  \end{itemize}

>>>>

  To further understand the nanoscopic structure of these membranes, there
  are several key questions which we intend to answer and will be laid out 
  and numbered in subsequent paragraphs.

  (1) Do monomers partition into and persist as defined monomer layers?
  H\textsubscript{II} and Col\textsubscript{h} phase LC membrane pores are 
  thought to be composed of monomer layers stacked on top of each other. 
  \begin{itemize}
  	\item Their existence is supported by experimental evidence of strong 
	$\pi$-$\pi$ stacking interactions in the direction perpendicular to the
	membrane plane.
	\item $\pi$-$\pi$ stacking will only occur between monomer head groups which
	leaves no description of what is happening in monomer tail region
	\item It is possible that $\pi$-$\pi$ stacking occurs vertically 
	with no order in reference to neighboring stacked columns of the same pore.  % BJC: not sure if this is actually true
	\item (1) Do monomers partition into and persist as defined monomer layers?
  \end{itemize}

  (2) If layers do exist, how many monomers constitute a single layer?
  There has been definitive answer to the question in literature.
%   We do not know the number of monomers that constitute the layers which stack
%   on top of each other to create pores.
  \begin{itemize}
%     \item The Col\textsubscript{h} phase is described as having pores made of
%     disks or layers stacked on top of one another, each containing a set 
%     number of monomers. 
    \item A simple simulation study of a similar molecule 
%MRS: suggests isn't the right word, since that implies it may still be valid, which probably isn't correct.  I would probably say how simple that test was, since what they did had almost no chance of getting the right answer in the proper context. We thought they did something reasonable, but they really didn't. 
%suggests
%BJC: Okay, added a little more to emphasize that what they did isn't really useful.
suggested
    that there are 4 monomers in each layer. Their estimation is based on a
    simulated system containing only 16 total monomers which likely does not sufficiently
    model the chemical environment present in the real system.~\cite{zhu_methacrylated_2006}. 
    \item A separate calculation based on the volume of the liquid crystal monomers proposes
    that there are seven monomers in each layer~\cite{resel_structural_2000}. 
    \item A molecular model has the best chance of directly answering this question.
  \end{itemize}
%MRS: phrasing
    %\item Once we know the number of monomers in each layer, we still do not know how

    (3) How do monomers in each layer position themselves with respect to surrounding 
    layers?
%     Even if we knew the number of monomers in each layer, we still would not know how 
%     monomers in each layer are positioned with respect to other layers. 
    \begin{itemize}
      \item A driving force of self assembly in this system is thought to be pi-pi
      stacking interactions between aromatic headgroups \cite{gazit_possible_2002}. 
      \item Gas phase ab initio studies of benzene dimers have shown a clear energetic
      advantage for parallel displaced and T-shaped pi-pi stacking conformations versus a
      sandwiched conformation ~\cite{sinnokrot_estimates_2002}.
      \item Substituted benzene rings exhibit an even stronger pi-pi stacking 
      attraction which favors the parallel displaced configuration in all cases
      except where the substitutions are extremely electron withdrawing
      \cite{waller_hybrid_2006,ringer_effect_2006}.
    \end{itemize}

@@

  (4) Can the system exist in other metastable states or phases that are not
  accessed during experiments?
  There remains the possibility that there is more than one metastable state 
  associated with a given LLC system.
  \begin{itemize}
    \item Simulating a membrane atomistically will require many atoms which further
    limits the timescales acessible with MD
    \item It is reasonable to expect that we will generate configurations which 
    are kinetically trapped in a metastable free energy basin
    \item We must be able to identify which state is produced experimentally
  \end{itemize}
